---
title: "Data Cleaning Sex Specific Foraging Frittilary FIG"
author: "Matthew Chmielewski"
date:  '`r format(Sys.time(), "%A, %d %B, %Y")`'
output: pdf_document
editor_options: 
  chunk_output_type:console
---
  
  Load Libraries
```{r}
packages <- c("xlsx", "dplyr", "purrr", "ggplot2")
suppressMessages(suppressWarnings(sapply(packages, require, character.only=TRUE, quietly=TRUE)))
```

Load data and check headings and check for truncation
```{r}
SSFFdata<-read.xlsx("Regal_ALL1998_2018.xlsx", sheetIndex=1)
head(SSFFdata)
length(SSFFdata$Year)
```
Check for spelling errors in plant binomials
```{r}
levels(SSFFdata$NectarPlantLatinName)
```

Fix typos/misspelled Plant binomials and common names
```{r}
SSFF_clean<-map_df(SSFFdata, ~ gsub("Achillea millifolium", "Achillea millefolium", .x))
SSFF_clean<-map_df(SSFF_clean, ~ gsub("Asclepias incarnata ", "Asclepias incarnata", .x))
SSFF_clean<-map_df(SSFF_clean, ~ gsub("Ascelpias incarnata", "Asclepias incarnata", .x))
SSFF_clean<-map_df(SSFF_clean, ~ gsub("Asclepias tuberosa ", "Asclepias tuberosa", .x))
SSFF_clean<-map_df(SSFF_clean, ~ gsub("Centaurea spp.", "Centaurea spp", .x))
SSFF_clean<-map_df(SSFF_clean, ~ gsub("Field Thistle ", "Field Thistle", .x))
SSFF_clean<-map_df(SSFF_clean, ~ gsub(" Common Milkweed", "Common Milkweed", .x))
SSFF_clean<-map_df(SSFF_clean, ~ gsub("Canada Thistle ", "Canada Thistle", .x))
SSFF_clean<-map_df(SSFF_clean, ~ gsub("Swamp milkweed", "Swamp Milkweed", .x))



SSFF_clean$NectarPlantLatinName<-as.factor(SSFF_clean$NectarPlantLatinName)
SSFF_clean$NectarPlantCommonName<-as.factor(SSFF_clean$NectarPlantCommonName)
SSFF_clean$Julian<-as.numeric(SSFF_clean$Julian)
SSFF_clean$Year<-as.factor(SSFF_clean$Year)


levels(SSFF_clean$NectarPlantLatinName)
levels(SSFF_clean$NectarPlantCommonName)
```

Examine conflicts between ID to genus vs species
```{r}
nrow(subset(SSFF_clean, SSFF_clean$NectarPlantLatinName == "Solidago spp/Centaurea spp"))
nrow(subset(SSFF_clean, SSFF_clean$NectarPlantLatinName == "Solidago spp"))
nrow(subset(SSFF_clean, SSFF_clean$NectarPlantLatinName == "Centaurea spp"))
nrow(subset(SSFF_clean, SSFF_clean$NectarPlantLatinName == "Cirsium spp"))
nrow(subset(SSFF_clean, SSFF_clean$NectarPlantLatinName == "Cirsium arvense"))
nrow(subset(SSFF_clean, SSFF_clean$NectarPlantLatinName == "Cirsium discolor"))
nrow(subset(SSFF_clean, SSFF_clean$NectarPlantLatinName == "Cirsium pumilum"))


```

*Solidago/Centaura* conflict seems best dealt with by dropping *Solidago spp/Centaurea spp* level (1 observation)
*Cirsium* conflicts difficult to resolve as *C. discolor*, *C. pumilum* and *Cirsium spp* contain many observations. 



Looking to the common names associated with *Cirsium spp* entries, it is possible to assign species to *Cirsium pumilum*.
```{r}

subset(SSFF_clean$NectarPlantLatinName, SSFF_clean$NectarPlantCommonName == "Pasture Thistle")

SSFF_clean %>% mutate(NectarPlantLatinName = replace(NectarPlantLatinName, NectarPlantCommonName=="Pasture Thistle", "Cirsium pumilum"))->SSFF2

subset(SSFF2$NectarPlantLatinName, SSFF2$NectarPlantCommonName == "Pasture Thistle")

SSFF2<-droplevels(SSFF2)

levels(SSFF2$NectarPlantLatinName)




```

Plot Phenology of Flowering By Species By Year
```{r}

pdf("phenology_by_year.pdf")

for (i in levels(SSFF2$Year)){
x<-paste("Flowering Phenology at FIG in", i, sep=" ")

plot(  
totalflowerpheno1<-ggplot(data=subset(SSFF2, SSFF2$Year == i), aes(Julian, NectarPlantLatinName)) +
  geom_point(fill = "darkgrey") +
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle(x)+
  xlab("Julian Date")+
  ylab("Flower Species"))


}

dev.off()

```

create mean first and last flowering dates for *C. discolor* and *C. pumilum*
```{r}
filter(SSFF_clean, NectarPlantLatinName == "Cirsium pumilum") %>%
  group_by(Year) %>%
  summarise(max = max(Julian))-> CPmax
CPmeanlast<-mean(CPmax$max)
CPmeanlast


filter(SSFF_clean, NectarPlantLatinName == "Cirsium discolor") %>%
  group_by(Year) %>%
  summarise(min = min(Julian))-> CDmin
CDmeanfirst<-mean(CDmin$min)
CDmeanfirst

```

plot phenology with bands showing average first and last flowering date for *C. pumilum* and *C. discolor*
```{r}

pdf("phenology_by_year2.pdf")

for (i in levels(SSFF2$Year)){
x<-paste("Flowering Phenology at FIG in", i, sep=" ")

plot(  
totalflowerpheno1<-ggplot(data=subset(SSFF2, SSFF2$Year == i), aes(Julian, NectarPlantLatinName)) +
  geom_point(fill = "darkgrey") +
  geom_vline(xintercept = CDmeanfirst, color = "blue")+
  geom_vline(xintercept = CPmeanlast, color = "purple")+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle(x)+
  xlab("Julian Date")+
  ylab("Flower Species"))


}

dev.off()

```


Write Datset to file
```{r}
write.xlsx(SSFF2, file = "SSFF_cleaned_5_18_2021.xlsx", sheetName="Cleaned SFFF Data")
ssffreadme<-"This dataset cleans the orginal data provided by dealing with input errors due to spelling and drops one genus-level ambiguity involving a Solidago spp/Centaurea spp. observation"
write.xlsx(ssffreadme, file = "SSFF_cleaned_5_18_2021.xlsx", sheetName="Readme", append = TRUE)
write.csv(SSFF_clean, file = "SSFFclass.csv")


```
