---
  title: "Assessing Sex-Specific Dissimilarities in Foraging Resource Use in Regal Fritillaries at FIG over 20 years"
author: "Matthew Chmielewski"
date:  '`r format(Sys.time(), "%A, %d %B, %Y")`'
output: pdf_document
editor_options: 
  chunk_output_type:console
---

 Load Libraries
```{r}
packages <- c("xlsx", "purrr", "ggplot2", "dplyr", "RColorBrewer", "cowplot", "vegan", "lme4", "bipartite", "lubridate", "tidyr")
suppressMessages(suppressWarnings(sapply(packages, require, character.only=TRUE, quietly=TRUE)))
```



load cleaned data, load classified Cirsium data, and replace old Cirsium spp values with newly classified values
```{r}
ssffdata<-read.xlsx("SSFF_cleaned_5_18_2021.xlsx", sheetIndex = 1)
cirsiumdata<-read.xlsx("cirsiumdata.xlsx", sheetIndex = 1)
ssffdata1<-as_tibble(filter(ssffdata, !grepl("Cirsium", NectarPlantLatinName)))

ssffdata1<-as.data.frame(ssffdata1)

nrow(ssffdata)-nrow(ssffdata1)
nrow(cirsiumdata)
ssffdata1$Duration<-as.numeric(ssffdata1$Duration)
cirsiumdata$StartSun<-as.factor(cirsiumdata$StartSun)
cirsiumdata$EndSun<-as.factor(cirsiumdata$EndSun)
cirsiumdata$StartWind<-as.factor(cirsiumdata$StartWind)
cirsiumdata$EndWind<-as.factor(cirsiumdata$EndWind)
cirsiumdata$EndTemp<-as.factor(cirsiumdata$EndTemp)
cirsiumdata$Behavior<-as.factor(cirsiumdata$Behavior)
cirsiumdata$NectarPlantLatinName<-cirsiumdata$consensus




ssff_data<-full_join(ssffdata1, cirsiumdata)
ssff_data<-subset(ssff_data, NectarPlantLatinName != "Cirsium spp")

ssff_data$fixeddate<-as.Date(as.numeric(ssff_data$Date), origin = "1899-12-30")
ssff_data$Date<-as.numeric(ssff_data$Date)
ssff_data$fixeddate<-as.Date(ssff_data$Date, origin = "1899-12-30")
ssff_data$week<-week(ssff_data$fixeddate)

ssff_data

ssff_data$Sex<-as.factor(ssff_data$Sex)
ssff_data$Year<-as.factor(ssff_data$Year)
```


plot each year's visitation by sex
```{r}

pdf("SSFF_annual_visitation.pdf")

for (i in levels(ssff_data$Year)){
x<-paste("Visitation Phenology at FIG in", i, sep=" ")
 
plot(totalflowerpheno1<-ggplot(data=subset(ssff_data, ssff_data$Year == i), aes(Julian, NectarPlantLatinName)) +
  geom_jitter(aes(fill = Sex), alpha = 0.6, shape = 21, size = 2) +
  scale_fill_manual(values = c("#D95F02", "#7570B3"))+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle(x)+
  xlab("Julian Date")+
  ylab("Flower Species"))



}

dev.off()

```


plot each year's visitation by sex on one page
```{r}

pdf("SSFF_annual_visitation2.pdf")

 
ggplot(data=ssff_data, aes(Julian, NectarPlantLatinName, fill = Sex)) +
  geom_jitter(alpha = 0.6, shape = 21, size = 2) +
  facet_wrap(~Year)+
  scale_fill_manual(values = c("#D95F02", "#7570B3"))+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  xlab("Julian Date")+
  ylab("Flower Species")




dev.off()
```


This section computes the observed Morisita-Horn dissimilarity index for the observed species association webs, and determines whether there is temporal correlation
```{r}

diffdata<-ssff_data %>% group_by(Site, Sex, Year, NectarPlantLatinName)  %>% summarise(n=length(NectarPlantLatinName))
diffdata


visitbyyear<-frame2webs(as.data.frame(diffdata), varnames = c("NectarPlantLatinName", "Sex", "Year", "n"))
visitbyyear

t(visitbyyear[[1]])


diffbyyear<-vector(mode = "list", length = length(visitbyyear))


for (i in 1:length(visitbyyear)){

  
  diffbyyear[i]<-as.list(vegdist(t(visitbyyear[[i]]), method = "horn"))
  
  
 

  
}

diffbyyear


mhdiss<-as.numeric(unlist(diffbyyear))

mhdiss<-as.data.frame(mhdiss)

mhdiss$year<-names(visitbyyear)
mhdiss

mhdiss$year<-as.numeric(mhdiss$year)


mhdistplot<-ggplot(data=mhdiss, aes(year, mhdiss)) +
  geom_point(alpha = 0.6, shape = 21, size = 3.5, fill = "DarkBlue") +
  geom_smooth(method = "lm", se = FALSE)+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("Male-Female Dissimilarity in Flower Visitation at FIG Over a 20 Year Period")+
  xlab("Year")+
  ylab("Morisita-Horn Dissimilarity")


mhdistplot

pdf("mgdistplot.pdf")
mhdistplot
dev.off()

```

*Full Dataset*

This section creates null distribution webs by shuffling the associations for each year randomly while keeping both the number of each plant species and the number of each butterfly sex the same. For each year 1000 of these webs are created.

This section then calculates the Morisita-Horn dissimilarity index for each of the null webs in order to generate a null mean and 95% CI. 

Finally, this plots null results relative to observed dissimilarity for each year. 
```{r}
nulltotalloop<-data.frame(matrix(nrow = 1000))
nullmeans<-c()
nullCI<-c()

for (z in 1:21){
testnull<-nullmodel(visitbyyear[[z]])

nulldifftest<-vector(mode = "list", length = length(testnull))
for (i in 1:length(testnull)){

  
  nulldifftest[i]<-as.list(vegdist(t(testnull[[i]]), method = "horn"))
}

nulldifftest
runvals<-unlist(nulldifftest)

nullmeans<-append(nullmeans, mean(runvals))
nullCI<-append(nullCI, 1.96*((sd(runvals)/sqrt(length(runvals)))))

nullmhdiss<-as.numeric(unlist(nulldifftest))
nullmhdiss<-as.data.frame(nullmhdiss, col.names = z)
nulltotalloop<-cbind(nulltotalloop, nullmhdiss)
}

nulltotalloop<-nulltotalloop[,-1]
colnames(nulltotalloop)<-names(visitbyyear)

nullbounds<-data.frame(matrix(nrow = 21))

nullbounds$nullmeans<-nullmeans
nullbounds$nullCI<-nullCI
nullbounds$year<-names(visitbyyear)
nullbounds<-nullbounds[,-1]

head(nullbounds)
nulltotalloop

nulltotalloop2<-gather(nulltotalloop, year)



head(nulltotalloop2)

nullmhdistboxplot<-ggplot(data=nulltotalloop2, aes(year, value)) +
  geom_boxplot(color = "DarkBlue")+
  #geom_errorbar(ymin = nullmean - nulldissCI, ymax = nullmean + nulldissCI, width = 0.02 )+
  geom_point(data=mhdiss, aes(as.factor(year), mhdiss), shape = 21, fill = "Red", size = 2)+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("Male-Female Dissimilarity in Flower Visitation at FIG Over a 20 Year Period")+
  xlab("Year")+
  ylab("Morisita-Horn Dissimilarity")


nullmhdistboxplot

pdf(file = "null model boxplot.pdf")
nullmhdistboxplot
dev.off()


nullmhdistplot<-ggplot(data=nullbounds, aes(year, nullmeans)) +
  geom_point(color = "DarkBlue")+
  geom_errorbar(ymin = nullmeans - nullCI, ymax = nullmeans + nullCI )+
  geom_point(data=mhdiss, aes(as.factor(year), mhdiss), shape = 21, fill = "Red", size = 2)+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("Male-Female Dissimilarity in Flower Visitation at FIG Over a 20 Year Period")+
  xlab("Year")+
  ylab("Morisita-Horn Dissimilarity")


nullmhdistplot

pdf(file = "null model mean and CI.pdf")
nullmhdistplot
dev.off()




```



*Overlap Truncation: Only includes data for the part of the year in which there are at least one female and male*

This truncated dataset deals with phenology by only including data from the period in which both females and males are present in the field.

```{r}


overlapdata<-ssff_data


outoverlap<-data.frame()

for (i in levels(overlapdata$Year)){
  
  overlapyear<-subset(overlapdata, Year == i)
        
  maleoverlap<-subset(overlapyear, Sex == "MALE")
  femaleoverlap<-subset(overlapyear, Sex == "FEMALE")
  
  malemax<-max(maleoverlap$Julian)
  femalemin<-min(femaleoverlap$Julian)
  
  annualoverlap<-subset(overlapyear, Julian >= femalemin & Julian <= malemax)


outoverlap<-rbind(outoverlap, annualoverlap)
  
  
}

outoverlap


plot(Julian~Sex, data=outoverlap)
plot(Julian~Sex, data=ssff_data)





```

Plotting data involving only considering dates when males and female overlap
```{r}
pdf("SSFF_annual_visitation_overlap.pdf")

for (i in levels(outoverlap$Year)){
x<-paste("Visitation Phenology of overlapping data at FIG in", i, sep=" ")
 
plot(totalflowerphenooverlap<-ggplot(data=subset(outoverlap, outoverlap$Year == i), aes(Julian, NectarPlantLatinName)) +
  geom_jitter(aes(fill = Sex), alpha = 0.6, shape = 21, size = 2) +
  scale_fill_manual(values = c("#D95F02", "#7570B3"))+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle(x)+
  xlab("Julian Date")+
  ylab("Flower Species"))



}

dev.off()


```



Create M-H dissimilarity for only data that overlap males and females
```{r}

diffdataoverlap<-outoverlap %>% group_by(Site, Sex, Year, NectarPlantLatinName)  %>% summarise(n=length(NectarPlantLatinName))
diffdataoverlap


visitbyyearoverlap<-frame2webs(as.data.frame(diffdataoverlap), varnames = c("NectarPlantLatinName", "Sex", "Year", "n"))
visitbyyearoverlap

t(visitbyyearoverlap[[1]])


diffbyyearoverlap<-vector(mode = "list", length = length(visitbyyearoverlap))


for (i in 1:length(visitbyyearoverlap)){

  
  diffbyyearoverlap[i]<-as.list(vegdist(t(visitbyyearoverlap[[i]]), method = "horn"))
  
  
 

  
}

diffbyyearoverlap


mhdissoverlap<-as.numeric(unlist(diffbyyearoverlap))

mhdissoverlap<-as.data.frame(mhdissoverlap)

mhdissoverlap$year<-names(visitbyyearoverlap)
mhdissoverlap

mhdissoverlap$year<-as.numeric(mhdissoverlap$year)


mhdistplotoverlap<-ggplot(data=mhdissoverlap, aes(year, mhdissoverlap)) +
  geom_point(alpha = 0.6, shape = 21, size = 3.5, fill = "DarkBlue") +
  geom_smooth(method = "lm", se = FALSE)+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("Male-Female Dissimilarity in Flower Visitation at FIG Over a 20 Year Period")+
  xlab("Year")+
  ylab("Morisita-Horn Dissimilarity")


mhdistplotoverlap

pdf("mgdistplotoverlap.pdf")
mhdistplotoverlap
dev.off()

summary(lm(mhdissoverlap~as.numeric(year), data = mhdissoverlap))

mhdissoverlap
```


This creates null distributions for overlap dataset. 
```{r}
nulltotalloopoverlap<-data.frame(matrix(nrow = 1000))
nullmeansoverlap<-c()
nullCIoverlap<-c()

for (z in 1:21){
testnulloverlap<-nullmodel(visitbyyearoverlap[[z]])

nulldifftestoverlap<-vector(mode = "list", length = length(testnulloverlap))
for (i in 1:length(testnulloverlap)){

  
  nulldifftestoverlap[i]<-as.list(vegdist(t(testnulloverlap[[i]]), method = "horn"))
}

nulldifftestoverlap
runvalsoverlap<-unlist(nulldifftestoverlap)

nullmeansoverlap<-append(nullmeansoverlap, mean(runvalsoverlap))
nullCIoverlap<-append(nullCIoverlap, 1.96*((sd(runvalsoverlap)/sqrt(length(runvalsoverlap)))))

nullmhdissoverlap<-as.numeric(unlist(nulldifftestoverlap))
nullmhdissoverlap<-as.data.frame(nullmhdissoverlap, col.names = z)
nulltotalloopoverlap<-cbind(nulltotalloopoverlap, nullmhdissoverlap)
}

nulltotalloopoverlap<-nulltotalloopoverlap[,-1]
colnames(nulltotalloopoverlap)<-names(visitbyyearoverlap)

nullboundsoverlap<-data.frame(matrix(nrow = 21))

nullboundsoverlap$nullmeansoverlap<-nullmeansoverlap
nullboundsoverlap$nullCIoverlap<-nullCIoverlap
nullboundsoverlap$year<-names(visitbyyearoverlap)
nullboundsoverlap<-nullboundsoverlap[,-1]

head(nullboundsoverlap)


nulltotalloop2overlap<-gather(nulltotalloopoverlap, year)

head(nulltotalloop2overlap)

nulltotalloop2overlap

nullmhdistboxplotoverlap<-ggplot(data=nulltotalloop2overlap, aes(year, value)) +
  geom_boxplot(color = "DarkBlue")+
  geom_point(data=mhdissoverlap, aes(as.factor(year), mhdissoverlap), shape = 21, fill = "Red", size = 2)+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("Male-Female Dissimilarity in Flower Visitation at FIG Over a 20 Year Period")+
  xlab("Year")+
  ylab("Morisita-Horn Dissimilarity")


nullmhdistboxplotoverlap

pdf(file = "null model boxplot.pdf")
nullmhdistboxplot
dev.off()

nullboundsoverlap

nullmhdistplotoverlap<-ggplot(data=nullboundsoverlap, aes(year, nullmeansoverlap)) +
  geom_point(color = "DarkBlue")+
  geom_errorbar(ymin = nullmeansoverlap - nullCIoverlap, ymax = nullmeansoverlap + nullCIoverlap)+
  geom_point(data=mhdissoverlap, aes(as.factor(year), mhdissoverlap), shape = 21, fill = "Red", size = 2)+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("Male-Female Dissimilarity in Flower Visitation at FIG Over a 20 Year Period for F-M overlap data")+
  xlab("Year")+
  ylab("Morisita-Horn Dissimilarity")


nullmhdistplotoverlap

pdf(file = "null model mean and CI overlap.pdf")
nullmhdistplotoverlap
dev.off()



mhcombined<-cbind(mhdissoverlap$mhdissoverlap, nullboundsoverlap)
names(mhcombined)<-c("observedmh", "nullmh", "nullCI", "year")
mhcombined
mhcombined1<-gather(mhcombined, "treat", "value", 1:2)
mhcombined1$nullCI[which(mhcombined1$treat == "observedmh")]<-0

mhcombined1

mhcolors<-c("lightpink3", "dodgerblue1", "Red", "DarkBlue")

nullmhdistplotcombinedoverlaptest<-ggplot(data=mhcombined1, aes(year, value)) +
  geom_point(aes(fill = treat), size = 3, shape = 21)+
  scale_fill_manual(values = mhcolors)+
  geom_vline(xintercept=seq(1.5, length(unique(nullboundsoverlap$year))-0.5, 1), lwd=0.5,linetype = 3, colour="gray")+
  theme_bw()+
  theme(axis.title.x = element_text(size  = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x  = element_text(angle=90, vjust=0.5, size =12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("")+
  xlab("Year")+
  ylab("Morisita-Horn Dissimilarity")


nullmhdistplotcombinedoverlaptest

nullbounds

nullmhdistplotcombinedoverlap<-ggplot(data=nullboundsoverlap, aes(year, nullmeansoverlap)) +
  geom_point(color = "lightpink3", size = 3)+
  geom_errorbar(ymin = nullmeansoverlap - nullCIoverlap, ymax = nullmeansoverlap + nullCIoverlap)+
  geom_point(data=mhdissoverlap, aes(as.factor(year), mhdissoverlap), shape = 21, fill = "Red", alpha = 0.7, size = 3)+
  geom_point(data=nullbounds, aes(year, nullmeans), color = "dodgerblue1",size = 3)+
  geom_errorbar(ymin = nullmeans - nullCI, ymax = nullmeans + nullCI)+
  geom_point(data=mhdiss, aes(as.factor(year), mhdiss), shape = 21, fill = "DarkBlue", alpha= 0.7, size = 3)+
  geom_vline(xintercept=seq(1.5, length(unique(nullboundsoverlap$year))-0.5, 1), lwd=0.5,linetype = 3, colour="gray")+
  theme_bw()+
  theme(axis.title.x = element_text(size  = 12),
    axis.title.y = element_text(size = 12),
    axis.text.x  = element_text(angle=90, vjust=0.5, size =12),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("")+
  xlab("Year")+
  ylab("Morisita-Horn Dissimilarity")


nullmhdistplotcombinedoverlap

pdf(file = "null model mean and CI combinedoverlap.pdf")
nullmhdistplotcombinedoverlap
dev.off()




```



This calculates effective species number and species richness for the full and subset datasets, and determines some basic statistics regarding ESN and richness 
```{r}

ESN<-data.frame()
richm<-data.frame()
richf<-data.frame()

for (d in 1:length(visitbyyear)){
  
div<-exp(diversity(t(visitbyyear[[d]])))

richnessm<-length(which(visitbyyear[[d]][,2] > 0))
richnessf<-length(which(visitbyyear[[d]][,1] > 0))

ESN<-rbind(ESN, div)

richm<-rbind(richm, richnessm)
richf<-rbind(richf, richnessf)
  
}

colnames(ESN)<-c("Female", "Male")
ESN<-gather(ESN, "Sex", "Species", 1:2)
ESN$Year<-names(visitbyyear)

colnames(richm)<-"richness"
colnames(richf)<-"richness"
ESN$richness<-as.numeric(unlist(rbind(richf, richm)))
ESN

mean(subset(ESN$richness, ESN$Sex == "Female"))

plot(Species~Sex, data = ESN, cex.lab = 2, cex.axis = 2)
plot(richness~Sex, data = ESN, cex.lab = 2, cex.axis = 2)



ESN$Sex<-as.factor(ESN$Sex)
ESNplot<-ggplot(data=ESN, aes(Year, Species)) +
  geom_point(aes(fill = Sex), alpha = 0.6, shape = 21, size = 2) +
  scale_fill_manual(values = c("#D95F02", "#7570B3"))+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("Effective Species Number Flowers Visited by Sex Over 20 Years at Fig")+
  xlab("Year")+
  ylab("Effective Species Number")

ESNplot

pdf("EffectiveSpeciesNumber.pdf")
ESNplot

dev.off()

anova(aov(Species~Year+Sex, data =ESN))



############################overlap

richoverlapm<-data.frame()
richoverlapf<-data.frame()
ESNoverlap<-data.frame()
for (d in 1:length(visitbyyearoverlap)){
  
divoverlap<-exp(diversity(t(visitbyyearoverlap[[d]])))
divoverlap

ESNoverlap<-rbind(ESNoverlap, divoverlap)
ESNoverlap


richnessoverlapm<-length(which(visitbyyearoverlap[[d]][,2] > 0))
richnessoverlapf<-length(which(visitbyyearoverlap[[d]][,1] > 0))

richoverlapm<-rbind(richoverlapm, richnessoverlapm)
richoverlapf<-rbind(richoverlapf, richnessoverlapf)
  
  
  
}

colnames(ESNoverlap)<-c("Female", "Male")
ESNoverlap<-gather(ESNoverlap, "Sex", "Species", 1:2)
ESNoverlap$Year<-names(visitbyyearoverlap)


colnames(richoverlapm)<-"richness"
colnames(richoverlapf)<-"richness"
ESNoverlap$richness<-as.numeric(unlist(rbind(richoverlapf, richoverlapm)))
ESNoverlap




ESNoverlapplot<-ggplot(data=ESNoverlap, aes(Year, Species)) +
  geom_point(aes(fill = Sex), alpha = 0.6, shape = 21, size = 2) +
  scale_fill_manual(values = c("#D95F02", "#7570B3"))+
  theme_bw()+
  theme(axis.title.x = element_text(),
    axis.title.y = element_text(),
    axis.text.x  = element_text(angle=90, vjust=0.5),
    panel.grid.minor.x=element_blank(),
    panel.grid.major.x=element_blank(),
    panel.grid.minor.y=element_blank(),
    panel.grid.major.y=element_blank(),
    plot.title = element_text())+
  ggtitle("Effective Species Number Flowers Visited by Sex Over 20 Years at Fig")+
  xlab("Year")+
  ylab("Effective Species Number")

ESNoverlapplot

pdf("EffectiveSpeciESNoverlapumber.pdf")
ESNoverlapplot

dev.off()


max(subset(ESN, ESN$Sex == "Female")$Species)
min(subset(ESN, ESN$Sex == "Female")$Species)

max(subset(ESN, ESN$Sex == "Male")$Species)
min(subset(ESN, ESN$Sex == "Male")$Species)

max(subset(ESN, ESN$Sex == "Female")$Species-subset(ESN, ESN$Sex == "Male")$Species)
min(subset(ESN, ESN$Sex == "Female")$Species-subset(ESN, ESN$Sex == "Male")$Species)
mean(subset(ESN, ESN$Sex == "Female")$Species-subset(ESN, ESN$Sex == "Male")$Species)
length(which((subset(ESN, ESN$Sex == "Female")$Species-subset(ESN, ESN$Sex == "Male")$Species)>0))
length(which((subset(ESN, ESN$Sex == "Female")$Species-subset(ESN, ESN$Sex == "Male")$Species)<0))




#total datset means and SE for ESN and richness
mean(subset(ESN$Species, ESN$Sex == "Male"))
sd(subset(ESN$Species, ESN$Sex == "Male"))/sqrt(21)
mean(subset(ESN$Species, ESN$Sex == "Female"))
sd(subset(ESN$Species, ESN$Sex == "Female"))/sqrt(21)

mean(subset(ESN$richness, ESN$Sex == "Male"))
sd(subset(ESN$richness, ESN$Sex == "Male"))/sqrt(21)
mean(subset(ESN$richness, ESN$Sex == "Female"))
sd(subset(ESN$richness, ESN$Sex == "Female"))/sqrt(21)


#overlap datset means and SE for ESN and richness
mean(subset(ESNoverlap$Species, ESNoverlap$Sex == "Male"))
sd(subset(ESNoverlap$Species, ESNoverlap$Sex == "Male"))/sqrt(21)
mean(subset(ESNoverlap$Species, ESNoverlap$Sex == "Female"))
sd(subset(ESNoverlap$Species, ESNoverlap$Sex == "Female"))/sqrt(21)

mean(subset(ESNoverlap$richness, ESNoverlap$Sex == "Male"))
sd(subset(ESNoverlap$richness, ESNoverlap$Sex == "Male"))/sqrt(21)
mean(subset(ESNoverlap$richness, ESNoverlap$Sex == "Female"))
sd(subset(ESNoverlap$richness, ESNoverlap$Sex == "Female"))/sqrt(21)



####change in mh for ms
changeinmh<-mhdiss$mhdiss-mhdissoverlap$mhdissoverlap
mean(changeinmh)
sd(changeinmh)

mhdiss

library(lme4)


anova(aov(Species~Year+Sex, data =ESN))

plot(Species~Year, data =ESNtest)
plot(richness~Year, data =ESN)

randomESNmod<-lmer(Species~Sex+(1|Year), data =ESN)
randomESNmod

plot(resid(randomESNmod))
plot(resid(lm(Species~Sex+Year, data = ESN)))
plot(Species~Year, data = ESN)

qqnorm(resid(lm(Species~Sex+Year, data = ESN)))

aov(Species~Year, data = ESN)
summary(lm(Species~Year, data = ESN))
summary(randomESNmod)
var(ESN$Species)

#################################################
#can get (very tiny) variance from deprecated nlme:lme, functionally the same as 0 from lme4:lmer (see https://rpubs.com/bbolker/6226)
library(nlme)

randomESNold<-lme(Species~Sex, random = ~1|Year, data = ESN)
randomESNold

summary(randomESNold)
varcovarrandom<-VarCorr(randomESNold)
varcovarrandom
varcovarsd<-varcovarrandom[,"StdDev"]
varcovarsd

as.numeric(varcovarrandom[1,"StdDev"])/as.numeric(varcovarrandom[2,"StdDev"])

randomrichnessold<-lme(richness~Sex, random = ~1|Year, data = ESN)
randomrichnessold

summary(randomrichnessold)


randomESNoverlap<-lme(Species~Sex, random = ~1|Year, data = ESNoverlap)
summary(randomESNoverlap)

randomrichnessoverlap<-lme(richness~Sex, random = ~1|Year, data = ESNoverlap)

summary(randomrichnessoverlap)


#within year variance is much greater than across year (whole dataset) variance
#within sex variance is comparatively relatively small when compared with whole dataset variance
#############################################

fullcontrastESN<-t.test(subset(ESN, ESN$Sex == "Male")$Species, subset(ESN, ESN$Sex == "Female")$Species, paired = TRUE)

overlapcontrastESN<-t.test(subset(ESNoverlap, ESNoverlap$Sex == "Male")$Species, subset(ESNoverlap, ESNoverlap$Sex == "Female")$Species, paired = TRUE)



fullcontrastrichness<-t.test(subset(ESN, ESN$Sex == "Male")$richness, subset(ESN, ESN$Sex == "Female")$richness, paired = TRUE)

overlapcontrastrichness<-t.test(subset(ESNoverlap, ESNoverlap$Sex == "Male")$richness, subset(ESNoverlap, ESNoverlap$Sex == "Female")$richness, paired = TRUE)

fullcontrastrichness

overlapcontrastrichness

```


Chi^2 for M vs. F visitations to flowers
```{r}

chi2fulldata<-ssffdata %>% group_by(Sex, NectarPlantLatinName) %>% tally(sort = TRUE)

chi2fulltable<-t(spread(chi2fulldata, NectarPlantLatinName, n)[,-1])
colnames(chi2fulltable)<-c("Female", "Male")

chi2fulltable[is.na(chi2fulltable)] = 0
chi2fulltable

resultsfull<-chisq.test(chi2fulltable)
resultsfull$observed
resultsfull$expected

round(resultsfull$residuals, 3)


write.csv(chi2fulldata, file = "visitationsummary.csv", row.names = FALSE)



annualvisitationsummary<-chi2fulldata<-ssffdata %>% group_by(Sex, NectarPlantLatinName, Year) %>% tally(sort = TRUE)
write.csv(annualvisitationsummary, file = "visitationsummarybyyear.csv", row.names = FALSE)
###############visualize relative magnitude of each plant-sex combo by plotting residuals
library(corrplot)

corrplot(resultsfull$residuals, is.corr = FALSE, col=colorRampPalette(c("#053061","white","#9f1228"))(300), tl.col = "black", cl.pos = "r", cl.ratio = 1.6, outline = TRUE)



#######################plot as percent contribution. 
contribfull<- 100*resultsfull$residuals^2/resultsfull$statistic
round(contribfull, 3)

sum(contribfull[,1])+sum(contribfull[,2])

corrplot(contribfull, is.corr = FALSE, col = "black", tl.col = "black", cl.pos = "n")



#overall chi2full is significant, and appears to be driven by mainly by asclepias tuberosa and cirsium discolor

pdf("chi2fulloutput.pdf")
corrplot(resultsfull$residuals, is.corr = FALSE, col=colorRampPalette(c("#053061","white","#9f1228"))(300), tl.col = "black", cl.pos = "r", cl.ratio = 1.6, outline = TRUE)
corrplot(contribfull, is.corr = FALSE, col = "black", tl.col = "black", cl.pos = "n")
dev.off()


corrplot(resultsfull$residuals, is.corr = FALSE, col=colorRampPalette(c("#053061","white","#9f1228"))(300), tl.col = "black", cl.pos = "n", outline = TRUE)
colorlegend(xlim=c(3,6), ylim=c(1,10), corrscale, signif(c(seq(-11.41,13.49,2.49)), 4), align="r", vertical=TRUE, addlabels=TRUE, cex= 0.75)



############################overlap dataset
chi2overlapdata<-outoverlap %>% group_by(Sex, NectarPlantLatinName) %>% tally(sort = TRUE)

chi2overlaptable<-t(spread(chi2overlapdata, NectarPlantLatinName, n)[,-1])
colnames(chi2overlaptable)<-c("Female", "Male")

chi2overlaptable[is.na(chi2overlaptable)] = 0
chi2overlaptable

resultsoverlap<-chisq.test(chi2overlaptable)
resultsoverlap$observed
resultsoverlap$expected

round(resultsoverlap$residuals, 3)

resultsoverlap

###############visualize relative magnitude of each plant-sex combo
corrplot(resultsoverlap$residuals, is.corr = FALSE, tl.col = "black", cl.pos = "n" )



#######################plot as percent contribution. 
contriboverlap<- 100*resultsoverlap$residuals^2/resultsoverlap$statistic
round(contriboverlap, 3)

sum(contriboverlap[,1])+sum(contriboverlap[,2])

corrplot(contriboverlap, is.corr = FALSE, col = "black", tl.col = "black", cl.pos = "n")

#overall chi2overlap is significant, and appears to be driven by mainly by asclepias tuberosa and cirsium discolor

pdf("chi2overlapoutput.pdf")
corrplot(resultsoverlap$residuals, is.corr = FALSE, col=colorRampPalette(c("#053061","white","#9f1228"))(300),tl.col = "black", cl.pos = "r", cl.ratio = 1.6, outline = TRUE)
corrplot(contriboverlap, is.corr = FALSE, col = "black", tl.col = "black", cl.pos = "n")
dev.off()

max(resultsoverlap$residuals)
corrscale<-colorRampPalette(c("#053061","white","#9f1228"))(300)

corrplot(resultsoverlap$residuals, is.corr = FALSE, col=colorRampPalette(c("#053061","white","#9f1228"))(300), tl.col = "black", cl.pos = "n", outline = TRUE)
colorlegend(xlim=c(3,6), ylim=c(1,10), corrscale, signif(c(seq(-7.51,7.63,1.514)), 3), align="r", vertical=TRUE, addlabels=TRUE, cex= 0.75)

pdf("chi2combinedrevised.pdf")
corrplot(resultsfull$residuals, is.corr = FALSE, col=colorRampPalette(c("#053061","white","#9f1228"))(300), tl.col = "black", cl.pos = "n", outline = TRUE)
colorlegend(xlim=c(3,6), ylim=c(1,10), corrscale, signif(c(seq(-11.41,13.49,2.49)), 4), align="r", vertical=TRUE, addlabels=TRUE, cex= 0.75)

corrplot(resultsoverlap$residuals, is.corr = FALSE, col=colorRampPalette(c("#053061","white","#9f1228"))(300), tl.col = "black", cl.pos = "n", outline = TRUE)
colorlegend(xlim=c(3,6), ylim=c(1,10), corrscale, signif(c(seq(-7.51,7.63,1.514)), 3), align="r", vertical=TRUE, addlabels=TRUE, cex= 0.75)
dev.off()
```

