---
title: "Fort Indiantown Gap Regal Frittilary nectar source analysis"
author: "Matthew Chmielewski"
date:  '`r format(Sys.time(), "%A, %d %B, %Y")`'
output: pdf_document
editor_options: 
  chunk_output_type:console
---

Load Libraries
```{r}
packages <- c("xlsx", "purrr", "ggplot2", "dplyr", "tidyr", "RColorBrewer", "cowplot", "vegan", "lme4", "ggfortify", "ggrepel", "car", "lsmeans", "nlme", "lmerTest", "wesanderson", "ggsci")
suppressMessages(suppressWarnings(sapply(packages, require, character.only=TRUE, quietly=TRUE)))
```

Read in PA and nectar concentration dataset, drop compounds with bad readings, add sex-association as a factor, write to file
```{r}
concdata<-read.xlsx("concdata.xlsx", sheetIndex  =1, header = TRUE)
concdata[is_empty(concdata)] = NA
head(concdata)
concdata2<-concdata[,-c(11,24,35,38,47,53)]
concdata2$Sex<-NA
concdata2[grep("Asclepias", concdata2$Species),]$Sex<-"Male"
concdata2$Sex[is.na(concdata2$Sex)]<-"Female"
write.csv(concdata2, file ="metaboliteconcdata.csv", row.names = FALSE)

```


Define amino acids and carbohydrates from the larger set of nectar compounds, then create dataframes for these sets of compounds
```{r}
aminos<-c("Arginine", "Asparagine", "Aspartate", "beta.Alanine", "Glutamine", "Glycine", "Isoleucine", "Leucine", "Lysine", "Methionine", "Ornithine", "Phenylalanine", "Proline", "Threonine", "Tryptophan", "Tyrosine", "Valine")
sugars<-c("Fructose", "Glucose", "Maltose", "Sucrose", "Trehalose")
sugarframe<-concdata[sugars]
sugarframe[is.na(sugarframe)] = 0
sugarframe$totalconc<-rowSums(sugarframe[sugars])
sugarframe$species<-as.factor(concdata$Species)

aminoframe<-concdata[aminos]
aminoframe[is.na(aminoframe)] = 0
aminoframe$totalconc<-rowSums(aminoframe[aminos])
aminoframe$species<-concdata$Species


```

Exploratory boxplots for carbohydrate concentrations by species
```{r}
pdf("sugarconcentrationsbyspecies.pdf")
for (i in names(sugarframe[,-7])){

x<-print(noquote(i))
plot(sugarbyspecies<-ggplot(data=sugarframe, aes_string("species", x)) +
geom_boxplot(fill = "gray")+
theme_bw()+
theme(axis.title.x = element_text(),
axis.title.y = element_text(),
axis.text.x  = element_text(angle=90, vjust=0.5),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
plot.title = element_text())+
ggtitle("")+
xlab("")+
ylab(i))
}
dev.off()
```

Summary of mean concentrations of compounds by species
````{r}
Fructosesummary<-sugarframe %>% group_by(species) %>% summarise(Fructose = mean(Fructose))
Sucrosesummary<-sugarframe %>% group_by(species) %>% summarise(Sucrose = mean(Sucrose))
Glucosesummary<-sugarframe %>% group_by(species) %>% summarise(Glucose = mean(Glucose))
Maltosesummary<-sugarframe %>% group_by(species) %>% summarise(Maltose = mean(Maltose))
Trehalosesummary<-sugarframe %>% group_by(species) %>% summarise(Trehalose = mean(Trehalose))
totalconcsugarssummary<-sugarframe %>% group_by(species) %>% summarise(totalconcsugars = mean(totalconc))

totalaminosummary<-aminoframe %>% group_by(species) %>% summarise(totalamimo = mean(totalconc)) 
prolinesummary<-aminoframe %>% group_by(species) %>% summarise(Proline = mean(Proline))
leucinesummary<-aminoframe %>% group_by(species) %>% summarise(Leucine = mean(Leucine))
glycinesummary<-aminoframe %>% group_by(species) %>% summarise(Glycine = mean(Glycine))

concentrationsummary<-left_join(Fructosesummary, Sucrosesummary)
concentrationsummary<-left_join(concentrationsummary, Glucosesummary)
concentrationsummary<-left_join(concentrationsummary, Maltosesummary)
concentrationsummary<-left_join(concentrationsummary, Trehalosesummary)
concentrationsummary<-left_join(concentrationsummary, totalconcsugarssummary)
concentrationsummary<-left_join(concentrationsummary, totalaminosummary)
concentrationsummary<-left_join(concentrationsummary, prolinesummary)
concentrationsummary<-left_join(concentrationsummary, leucinesummary)
concentrationsummary<-left_join(concentrationsummary, glycinesummary)

concentrationsummary

write.csv(concentrationsummary, file = "summaryofconcentrations.csv")
```


Plots of amino acid concentrations by plant species
```{r}
pdf("aminoacidconcentrationsbyspecies.pdf")
for (i in names(aminoframe[,-19])){
x<-print(noquote(i))
plot(aminobyspecies<-ggplot(data=aminoframe, aes_string("species", x)) +
geom_boxplot(fill = "gray")+
theme_bw()+
theme(axis.title.x = element_text(),
axis.title.y = element_text(),
axis.text.x  = element_text(angle=90, vjust=0.5),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
plot.title = element_text())+
ggtitle("")+
xlab("")+
ylab(i))
}
dev.off()
```

Create  PCA plots in order to explore the data as well as identify potential outliers, which were eventually be dropped from the final analysis
```{r}

################PCA with all usable values
head(concdata)
PCAdataconctotal<-concdata[,-c(19,38,53)] #drop columns with negative values

PCAdataconctotal<-PCAdataconctotal[ , colSums(is.na(PCAdataconctotal)) == 0] #remove columns with NA values
head(PCAdataconctotal)

PCAconctotal<-prcomp(PCAdataconctotal[,c(-1,-2)], scale. = TRUE) # create PCA
summary(PCAconctotal)

#plot PCA
PCAtotalconc<-autoplot(PCAconctotal, data = PCAdataconctotal, shape = 21, label = TRUE, fill = "Species", alpha = 0.6, frame = TRUE, frame.type = "t", frame.colour = "Species")+theme_bw()

PCAtotalconc

#sample rows 30 and 38 are large and huge outliers along PC1 (30 becomes an outlier once 38 is dropped)

concdata[38,]
################PCA with above outliers rows 30 and 38 removed (2036oA_38 and 2036oA_45)


PCAdataconcsubset<-concdata[-c(30,38),-c(19,38, 53)] #drop columns with negative values

PCAdataconcsubset<-PCAdataconcsubset[ , colSums(is.na(PCAdataconcsubset)) == 0] #remove columns with NA values
head(PCAdataconcsubset)
rownames(PCAdataconcsubset)<-PCAdataconcsubset$file_name

PCAconcsubset<-prcomp(PCAdataconcsubset[,c(-1,-2)], scale. = TRUE) # create PCA
summary(PCAconcsubset)


#plot PCA without row numbers and with ellipses

multispeciesPCA<-autoplot(PCAconcsubset, data = PCAdataconcsubset, shape = 21, fill = "Species", frame = TRUE, frame.type = "norm", frame.colour = "Species", alpha = 0.6, size =3)+theme_bw()

multispeciesPCA

#plot PCA with sample labels
multiPCAsample<-autoplot(PCAconcsubset, data = PCAdataconcsubset, label = FALSE, shape = 21, size =2, fill = "Species", alpha = 0.6)+theme_bw()+geom_text_repel( label = rownames(PCAdataconcsubset)) 

multiPCAsample

PCAconcsubset
#plot PCA with loadings
multiPCAloadings<-autoplot(PCAconcsubset, data = PCAdataconcsubset, shape = 21, fill = "Species", loadings = TRUE, loading.type = "norm", loadings.label = TRUE,  alpha = 0.6, size =3)+theme_bw()

multiPCAloadings

bottom<-plot_grid(multispeciesPCA, multiPCAsample, ncol = 2)
multinectar3panel<-plot_grid(multiPCAloadings, bottom, ncol = 1)

pdf(file="multiplots.pdf", paper= "a4r", width = 11)
PCAtotalconc
multispeciesPCA
multiPCAsample
multiPCAloadings
dev.off()

asyriacadata<-subset(PCAdataconctotal, Species == "Asclepias syriaca")
rownames(asyriacadata)<-asyriacadata$file_name
atuberosadata<-subset(PCAdataconctotal, Species == "Asclepias tuberosa")
rownames(atuberosadata)<-atuberosadata$file_name
cstoebedata<-subset(PCAdataconctotal, Species == "Centaurea stoebe")
rownames(cstoebedata)<-cstoebedata$file_name
cdiscolordata<-subset(PCAdataconctotal, Species == "Cirsium discolor")
rownames(cdiscolordata)<-cdiscolordata$file_name
cpumilumdata<-subset(PCAdataconctotal, Species == "Cirsium pumilum")
rownames(cpumilumdata)<-cpumilumdata$file_name
mfistulosadata<-subset(PCAdataconctotal, Species == "Monarda fistulosa")
rownames(mfistulosadata)<-mfistulosadata$file_name


asyriacapca<-prcomp(asyriacadata[,c(-1,-2)], scale. = TRUE) 
atuberosapca<-prcomp(atuberosadata[,c(-1,-2)], scale. = TRUE) 
cstoebepca<-prcomp(cstoebedata[,c(-1,-2)], scale. = TRUE) 
cdiscolorpca<-prcomp(cdiscolordata[,c(-1,-2)], scale. = TRUE) 
cdiscolorpca<-prcomp(cdiscolordata[,c(-1,-2)], scale. = TRUE) 
cpumilumpca<-prcomp(cpumilumdata[,c(-1,-2)], scale. = TRUE) 
mfistulosapca<-prcomp(mfistulosadata[,c(-1,-2)], scale. = TRUE) 


asyriacaplot<-autoplot(asyriacapca, data = asyriacadata, shape = 21, label = TRUE, fill = "Species", alpha = 0.6, frame = TRUE, frame.type = "t", frame.colour = "Species", )+theme_bw()
asyriacaplot

atuberosaplot<-autoplot(atuberosapca, data = atuberosadata, shape = 21, label = TRUE, fill = "Species", alpha = 0.6, frame = TRUE, frame.type = "t", frame.colour = "Species", )+theme_bw()
atuberosaplot

cstoebeplot<-autoplot(cstoebepca, data = cstoebedata, shape = 21, label = TRUE, fill = "Species", alpha = 0.6, frame = TRUE, frame.type = "t", frame.colour = "Species", )+theme_bw()
cstoebeplot

cdiscolorplot<-autoplot(cdiscolorpca, data = cdiscolordata, shape = 21, label = TRUE, fill = "Species", alpha = 0.6, frame = TRUE, frame.type = "t", frame.colour = "Species", )+theme_bw()
cdiscolorplot

cpumilumplot<-autoplot(cpumilumpca, data = cpumilumdata, shape = 21, label = TRUE, fill = "Species", alpha = 0.6, frame = TRUE, frame.type = "t", frame.colour = "Species", )+theme_bw()
cpumilumplot

mfistulosaplot<-autoplot(mfistulosapca, data = mfistulosadata, shape = 21, label = TRUE, fill = "Species", alpha = 0.6, frame = TRUE, frame.type = "t", frame.colour = "Species", )+theme_bw()
mfistulosaplot

pdf(file = "speciesPCAplots.pdf", paper = "a4r", width= 11)
asyriacaplot
atuberosaplot
cstoebeplot
cpumilumplot
cdiscolorplot
mfistulosaplot
dev.off()

#subset dataset based on PCA outliers
PCAdataconctotal[c(13,30,38,59,73),]
finalconcsubset<-PCAdataconctotal[-c(13,30,38,59,73),]

finalconcsubset1<-finalconcsubset[ , colSums(is.na(finalconcsubset)) == 0]

PCAfinal<-prcomp(finalconcsubset1[,c(-1,-2)], scale. = TRUE) # create PCA
summary(PCAfinal)

#plot PCA without row numbers and with ellipses

finalPCAplot<-autoplot(PCAfinal, data = finalconcsubset1, shape = 21, fill = "Species", frame = TRUE, frame.type = "norm", frame.colour = "Species", alpha = 0.6, size =3)+theme_bw()

finalPCAplot

finalconcsubset2<-finalconcsubset1
finalconcsubset2$sex<-finalconcsubset2$Species


finalconcsubset2$sex[finalconcsubset2$Species == "Asclepias syriaca"]<-"M"
finalconcsubset2$sex[finalconcsubset2$Species == "Asclepias tuberosa"]<-"M"
finalconcsubset2$sex[finalconcsubset2$sex != "M"] = "F"
finalconcsubset2$sex<-as.factor(finalconcsubset2$sex)

finalconcsubset2

write.csv(finalconcsubset2, "finalconcentrationnooutliers.csv")

#plot PCA by sex
PCAfinalsex<-prcomp(finalconcsubset2[,c(-1,-2,-48)], scale. = TRUE) # create PCA
summary(PCAfinalsex)


finalPCAplotsex<-autoplot(PCAfinalsex, data = finalconcsubset2, shape = 21, fill = "sex", frame = TRUE, frame.type = "norm", frame.colour = "sex", alpha = 0.6, size =3)+theme_bw()+ggtitle("All Compounds")

finalPCAplotsex


############PCA plots for sugars, AAs
PCAsugarframe<-sugarframe[-c(13,30,38,59,73),]

PCAsugarframe$sex<-as.character(PCAsugarframe$species)
PCAsugarframe$sex[as.character(PCAsugarframe$species) == "Asclepias syriaca"]<-"M"
PCAsugarframe$sex[as.character(PCAsugarframe$species) == "Asclepias tuberosa"]<-"M"
PCAsugarframe$sex[as.character(PCAsugarframe$sex) != "M"]<-"F"
(PCAsugarframe)
PCAaminoframe<-aminoframe


PCAsugarsex<-prcomp(PCAsugarframe[,c(-6,-7,-8)], scale. = TRUE) # create PCA
summary(PCAsugarsex)


PCAplotsugarsex<-autoplot(PCAsugarsex, data =PCAsugarframe, shape = 21, fill = "sex", frame = TRUE, frame.type = "norm", frame.colour = "sex", alpha = 0.6, size =3)+theme_bw()+ggtitle("Sugars")

PCAplotsugarsex


PCAaminoframe<-aminoframe[-c(13,30,38,59,73),]

PCAaminoframe$sex<-as.character(PCAaminoframe$species)
PCAaminoframe$sex[as.character(PCAaminoframe$species) == "Asclepias syriaca"]<-"M"
PCAaminoframe$sex[as.character(PCAaminoframe$species) == "Asclepias tuberosa"]<-"M"
PCAaminoframe$sex[as.character(PCAaminoframe$sex) != "M"]<-"F"


PCAaminosex<-prcomp(PCAaminoframe[,c(-12,-18,-19,-20)], scale. = TRUE) # create PCA
summary(PCAaminosex)


PCAplotaminosex<-autoplot(PCAaminosex, data =PCAaminoframe, shape = 21, fill = "sex", frame = TRUE, frame.type = "norm", frame.colour = "sex", alpha = 0.6, size =3)+theme_bw()+ggtitle("Amino Acids")

PCAplotaminosex

pdf("PCAsbysex.pdf")
finalPCAplotsex
PCAplotsugarsex
PCAplotaminosex
dev.off()
```

Using information from the PCAs created above, outliers identified and new dataframes without those outliers generated
```{r}
newaminos<-c("Arginine", "Asparagine", "Aspartate", "beta.Alanine", "Glutamine", "Glycine", "Isoleucine", "Leucine", "Lysine", "Methionine", "Ornithine", "Proline", "Threonine", "Tryptophan", "Tyrosine", "Valine")
newoligosaccharides<-c("Fructose", "Galactinol", "Glucose", "Maltose", "Sucrose")
newsugars<-c("Fructose", "Galactinol", "Glucose", "Maltose", "myo.Inositol", "Sucrose", "Threonate")
finaloligosaccharideframe<-finalconcsubset1[newoligosaccharides]
finaloligosaccharideframe[is.na(finaloligosaccharideframe)] = 0
finaloligosaccharideframe$totalconc<-rowSums(finaloligosaccharideframe[newoligosaccharides])
finaloligosaccharideframe$species<-as.factor(finalconcsubset1$Species)
levels(finaloligosaccharideframe$species)
finalaminoframe<-finalconcsubset1[newaminos]
finalaminoframe[is.na(finalaminoframe)] = 0
finalaminoframe$totalconc<-rowSums(finalaminoframe[newaminos])
finalaminoframe$species<-finalconcsubset1$Species
finalaminoframe
finalsugarframe<-finalconcsubset1[newsugars]
finalsugarframe[is.na(finalsugarframe)] = 0
finalsugarframe$totalconc<-rowSums(finalsugarframe[newsugars])
finalsugarframe$species<-finalconcsubset1$Species
finalsugarframe

finalframenooutliers<-cbind(finalsugarframe, finalaminoframe)
write.csv(finalframenooutliers, "finalframenooutlier.csv")
```


Plot carbohydrates of interest by species after dropping outliers
```{r}
pdf("oligosaccharidesbyspeciesnooutliers.pdf")
for (i in names(finaloligosaccharideframe[,-7])){
x<-print(noquote(i))
plot(finaloligosaccharidesbyspecies<-ggplot(data=finaloligosaccharideframe, aes_string("species", x)) +
geom_boxplot(fill = "gray")+
#scale_fill_manual(values = c("#D95F02", "#7570B3"))+
theme_bw()+
theme(axis.title.x = element_text(),
axis.title.y = element_text(),
axis.text.x  = element_text(angle=90, vjust=0.5),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
plot.title = element_text())+
ggtitle("")+
xlab("")+
ylab(i))
}
dev.off()
```

Plot amino acids without outliers
```{r}
pdf("AAbyspeciesnooutliers.pdf")
for (i in names(finalaminoframe[,-18])){
x<-print(noquote(i))
plot(finalaminobyspecies<-ggplot(data=finalaminoframe, aes_string("species", x)) +
geom_boxplot(fill = "gray")+
#scale_fill_manual(values = c("#D95F02", "#7570B3"))+
theme_bw()+
theme(axis.title.x = element_text(),
axis.title.y = element_text(),
axis.text.x  = element_text(angle=90, vjust=0.5),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
plot.title = element_text())+
ggtitle("")+
xlab("")+
ylab(i))
}
dev.off()

```

Plot all of the carbohydrates with no outliers
```{r}
pdf("sugarsbyspeciesnooutliers.pdf")
for (i in names(finalsugarframe[,-9])){
x<-print(noquote(i))
plot(finalsugarsbyspecies<-ggplot(data=finalsugarframe, aes_string("species", x)) +
geom_boxplot(fill = "gray")+
#scale_fill_manual(values = c("#D95F02", "#7570B3"))+
theme_bw()+
theme(axis.title.x = element_text(),
axis.title.y = element_text(),
axis.text.x  = element_text(angle=90, vjust=0.5),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
plot.title = element_text())+
ggtitle("")+
xlab("")+
ylab(i))
}
dev.off()
```

welch's ANOVA/t (defaults to var.equal = FALSE and therefore Welch's test, and t = ANOVA in comparison of two catergory (m vs.f))
```{r}

t.test(totalconc~sex, data =finalsugarframesex)

#given number of tests across individual compounds here, alpha = 0.007 via bonferroni correction
t.test(Glucose~sex, data =finalsugarframesex)
t.test(Fructose~sex, data =finalsugarframesex)
t.test(myo.Inositol~sex, data =finalsugarframesex)
t.test(Sucrose~sex, data =finalsugarframesex)
t.test(Galactinol~sex, data =finalsugarframesex)
t.test(Maltose~sex, data =finalsugarframesex)
t.test(Threonate~sex, data =finalsugarframesex)

t.test(totalconc~sex, data =finalaminoframesex)

#given number of tests across individual compounds here, alpha = 0.0167 via bonferroni correction
t.test(Proline~sex, data =finalaminoframesex)
t.test(Leucine~sex, data =finalaminoframesex)
t.test(Glycine~sex, data =finalaminoframesex)
```

Plotting final boxplots to aggregate for figure output
```{r}
finalsugarframesex
head(finalaminoframesex)

sugarlong<-gather(finalsugarframesex, compound, value, Fructose:totalconc)
sugarlong$compound[sugarlong$compound == "totalconc"]<-"total"
aminolong<-gather(finalaminoframesex, compound, value, Arginine:totalconc)
aminolong$compound[which(aminolong$compound == "totalconc")]<-"total"


selectaminos<-c("Leucine", "Glycine", "Proline", "totalconc")
aminotargets<-subset(aminolong, aminolong$compound == selectaminos)
aminotargets$compound[aminotargets$compound == "totalconc"] <-"total"
aminotargets$compound<-factor(aminotargets$compound, levels = c("Leucine", "Glycine", "Proline", "total"))

colorvals<-c("dodgerblue3", "dodgerblue3", "sienna3", "sienna3", "sienna3", "sienna3")

colorvals<-c("#3B9AB2", "#3B9AB2", "#F21A00","#F21A00","#F21A00","#F21A00")

labelvals<-c("Asy", "Atu", "Cst", "Cdi", "Cpu", "Mfi")
female = intToUtf8(9792)
male = intToUtf8(9794)


subset(aminolong, aminolong$species == "Asclepias tuberosa" & aminolong$compound == "Glycine")
subset(aminotargets, aminotargets$species == "Asclepias tuberosa")


totalsugarboxplot<-ggplot(data=subset(sugarlong, sugarlong$compound == "total"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_blank(),
plot.margin = unit(c(0,1,0.5,1), "cm"))+
ggtitle("Total")+
xlab("")+
ylab("Total")

totalsugarboxplot


sugartotalfinal<-totalsugarboxplot+
geom_text(label = female, x=6, y = 1100000, size = 10)+
geom_text(label = male, x = 1, y = 1100000, size = 10)+
geom_text(label = "*", x = 2.5, y = 1100000, size = 10)


sugartotalfinal

   



glucoseboxplot<-ggplot(data=subset(sugarlong, sugarlong$compound == "Glucose"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_blank(),
plot.margin = unit(c(0,1,0.5,1), "cm"))+
ggtitle("")+
xlab("")+
ylab("Glucose")

glucoseboxplot

glucosefinal<-glucoseboxplot+
geom_text(label = female, x=6, y = 550000, size = 10)+
geom_text(label = male, x = 1, y = 550000, size = 10)+
geom_text(label = "*", x = 2.5, y = 550000, size = 10)
   
   
glucosefinal



Sucroseboxplot<-ggplot(data=subset(sugarlong, sugarlong$compound == "Sucrose"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_blank(),
plot.margin = unit(c(0,1,0.5,1), "cm"))+
ggtitle("")+
xlab("")+
ylab("Sucrose")

Sucroseboxplot

Sucrosefinal<-ggdraw() +draw_plot(Sucroseboxplot)
  
   
Sucrosefinal


Fructoseboxplot<-ggplot(data=subset(sugarlong, sugarlong$compound == "Fructose"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_blank(),
plot.margin = unit(c(0,1,0.5,1), "cm"))+
ggtitle("")+
xlab("")+
ylab("Fructose")

Fructoseboxplot

fructosefinal<-Fructoseboxplot+
geom_text(label = "*", x = 2.5, y = 280000, size = 10)
   
   

 
   
fructosefinal



Galactinolboxplot<-ggplot(data=subset(sugarlong, sugarlong$compound == "Galactinol"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_text(face = "bold", size = 16),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_blank(),
plot.margin = unit(c(0,1,0.5,1), "cm"))+
ggtitle("")+
xlab("")+
ylab("Galactinol")

Galactinolboxplot

galactinolfinal<-Galactinolboxplot+
geom_text(label = "*", x = 2.5, y = 1600, size = 10)
   
   
galactinolfinal


Maltoseboxplot<-ggplot(data=subset(sugarlong, sugarlong$compound == "Maltose"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_blank(),
plot.margin = unit(c(0,1,0.5,1), "cm"))+
ggtitle("")+
xlab("")+
ylab("Maltose")

Maltoseboxplot

Maltosefinal<-ggdraw() +draw_plot(Maltoseboxplot)
 
    
Maltosefinal



Threonateboxplot<-ggplot(data=subset(sugarlong, sugarlong$compound == "Threonate"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_blank(),
plot.margin = unit(c(0,1,0.5,1), "cm"))+
ggtitle("")+
xlab("")+
ylab("Threonate")

Threonateboxplot

threonatefinal<-Threonateboxplot+
geom_text(label = "*", x = 2.5, y = 130, size = 10)
   
threonatefinal
  
   




myo.Inositolboxplot<-ggplot(data=subset(sugarlong, sugarlong$compound == "myo.Inositol"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_text(face = "bold", size = 16),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_blank(),
plot.margin = unit(c(0,1,0.5,1), "cm"))+
ggtitle("")+
xlab("")+
ylab("myo.Inositol")

myo.Inositolboxplot

myo.Inositolfinal<-ggdraw() +draw_plot(myo.Inositolboxplot)
  
   
myo.Inositolfinal


totalaminoboxplot<-ggplot(data=subset(aminotargets, aminotargets$compound == "total"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.y = element_text(face = "bold", size = 16),
axis.text.x  = element_blank(),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 12, hjust = 0.5))+
ggtitle("")+
xlab("")+
ylab("Total")

aminototalfinal<-totalaminoboxplot+geom_text(label = female, x=6, y = 18000, size = 10)+
geom_text(label = male, x = 1, y = 18000, size = 10)+
geom_text(label = "*", x = 2.5, y = 18000, size = 10)
  
aminototalfinal  


Leucineboxplot<-ggplot(data=subset(aminotargets, aminotargets$compound == "Leucine"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_text(face = "bold", size = 16),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 12, hjust = 0.5))+
ggtitle("")+
xlab("")+
ylab("Leucine")

Leucinefinal<-Leucineboxplot+geom_text(label = female, x=6, y = 21.5, size = 10)+
geom_text(label = male, x = 1, y = 21.5, size = 10)+
geom_text(label = "*", x = 2.5, y = 21.5, size = 10)
 
Leucinefinal
  


Prolineboxplot<-ggplot(data=subset(aminotargets, aminotargets$compound == "Proline"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.y = element_text(face = "bold", size = 16),
axis.text.x  = element_blank(),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 12, hjust = 0.5))+
ggtitle("")+
xlab("")+
ylab("Proline")

Prolineboxplot

Prolinefinal<-Prolineboxplot+geom_text(label = female, x=6, y = 48, size = 10)+
geom_text(label = male, x = 1, y = 48, size = 10)+
geom_text(label = "*", x = 2.5, y = 48, size = 10)
 
Prolinefinal
  
  


Glycineboxplot<-ggplot(data=subset(aminotargets, aminotargets$compound == "Glycine"), aes(species, value)) +
geom_boxplot(aes(fill = species))+
scale_fill_manual(values = colorvals)+
scale_x_discrete(labels = labelvals)+
geom_vline(xintercept = 2.5, linetype = "dashed")+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 18, hjust = 0.5),
axis.text.x  = element_text(face = "bold", size = 16),
axis.text.y = element_text(face = "bold", size = 16),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 12, hjust = 0.5))+
ggtitle("")+
xlab("")+
ylab("Glycine")

Glycinefinal<-Glycineboxplot+geom_text(label = female, x=6, y = 50, size = 10)+
geom_text(label = male, x = 1, y = 50, size = 10)+
geom_text(label = "*", x = 2.5, y = 50, size = 10)

  
  

Glycinefinal


aminoupdate<-plot_grid(aminototalfinal, Prolinefinal, Glycinefinal, Leucinefinal, NULL, NULL, NULL, NULL, align = "hv", ncol= 2)
aminoupdate


sugarupdate<-plot_grid(sugartotalfinal, glucosefinal, Fructoseboxplot, Sucroseboxplot, Maltoseboxplot, threonatefinal, myo.Inositolboxplot, galactinolfinal, align = "hv", ncol = 2)
sugarupdate

sugarfigure<-ggdraw()+
draw_plot(sugarupdate)+
draw_text(text = female, size = 30, hjust = -20, vjust = -13.5)+ 
draw_text(text = male, size = 30, hjust = 18, vjust = -13.5)+
draw_text(text = female, size = 30, hjust = 1.5, vjust = -13.5)+ 
draw_text(text = male, size = 30, hjust = -3.5, vjust = -13.5)+
draw_text("*", size= 30, vjust = -14.5, hjust = 23.15)+
draw_text("*", size= 30, vjust = -14.5, hjust = -16.85)+
draw_text("*", size= 30, vjust = -5.5, hjust = 23.15)


draw_text("*", size= 30, vjust = -14.5, hjust = 23.15)
draw_text("*", size= 30, vjust = -14.5, hjust = 23.15)
draw_text("*", size= 30, vjust = -14.5, hjust = 23.15)

sugarfigure




+draw_line(x = c(0.15, 0.25), y = 0.95, color = "deepskyblue2", size = 1)+ draw_line(x = c(0.15, 0.25), y = 0.7, color = "deepskyblue2", size = 1) + draw_line(x = c(0.15, 0.25), y = 0.45, color = "deepskyblue2", size = 1)+ draw_line(x = c(0.15, 0.25), y = 0.2, color = "deepskyblue2", size = 1) +
  
draw_line(x = c(0.65, 0.75), y = 0.95, color = "deepskyblue2", size = 1) + draw_line(x = c(0.65, 0.75), y = 0.7, color = "deepskyblue2", size = 1) + draw_line(x = c(0.65, 0.75), y = 0.45, color = "deepskyblue2", size = 1)+ draw_line(x = c(0.65, 0.75), y = 0.2, color = "deepskyblue2", size = 1)+
  
draw_line(x = c(0.26, 0.43), y = 0.95, color = "goldenrod2", size = 1)+ draw_line(x = c(0.26, 0.43), y = 0.7, color = "goldenrod2", size = 1) + draw_line(x = c(0.26, 0.43), y = 0.45, color = "goldenrod2", size = 1)+ draw_line(x = c(0.26, 0.43), y = 0.2, color = "goldenrod2", size = 1) +

draw_line(x = c(0.76, 0.94), y = 0.95, color = "goldenrod2", size = 1) + draw_line(x = c(0.76, 0.94), y = 0.7, color = "goldenrod2", size = 1) + draw_line(x = c(0.76, 0.94), y = 0.45, color = "goldenrod2", size = 1)+ draw_line(x = c(0.76, 0.94), y = 0.2, color = "goldenrod2", size = 1)


sugarfigure

png("sugartotaloutput.png",width = 300, height = 225, units='mm', res = 400)
sugarfigure
dev.off()


png("aminototaloutput.png", width = 300, height = 225, units = 'mm', res = 400)
aminofigure
dev.off()


aminogrid<-plot_grid(aminototalfinal, Leucinefinal, Glycinefinal, Prolinefinal, align = "hv")

sugargrid<-plot_grid(sugartotalfinal, glucosefinal, fructosefinal, Sucrosefinal, Maltosefinal, threonatefinal, myo.Inositolfinal, Galactinolfinal, ncol = 2)

aminogrid





png("aminofinal.png", width = 465, height = 225, units='mm', res = 300)
aminofinal
dev.off()

png("sugarfinal.png", width = 465, height = 225, units='mm', res = 300)
sugarfinal
dev.off()





aminoboxplot<-ggplot(data=aminotargets, aes(species, value)) +
geom_boxplot(aes(fill = species))+
facet_grid(rows = vars(compound), scales = "free_y")+
scale_fill_uchicago(alpha = 0.5)+
theme_bw()+
theme(axis.title.x = element_text(),
axis.title.y = element_text(size =12, face = "bold"),
axis.text.x  = element_text(size = 12, face = "bold", angle = 90),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
plot.title = element_text(),
legend.position = "none")+
ggtitle("")+
xlab("")+
ylab("Concentration (ng/uL)")

aminoboxplot



sugarboxplot<-ggplot(data=sugarlong, aes(species, value)) +
geom_boxplot(aes(fill = species))+
facet_grid(rows = vars(compound), scales = "free_y")+
scale_fill_uchicago(alpha = 0.5)+
theme_bw()+
theme(axis.title.x = element_text(),
axis.title.y = element_text(size =12, face = "bold"),
axis.text.x  = element_text(size = 12, face = "bold", angle = 90),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
plot.title = element_text(),
legend.position = "none")+
ggtitle("")+
xlab("")+
ylab("Concentration (ng/uL)")

sugarboxplot


female = intToUtf8(9792)
male = intToUtf8(9794)


plot(Proline~Leucine, data = finalaminoframe)
plot(Proline~Glycine, data = finalaminoframe)
plot(Proline~totalconc, data = finalaminoframe)

summary(lm(Proline~Leucine, data = finalaminoframe))
summary(lm(Proline~Glycine, data = finalaminoframe))
summary(lm(Proline~totalconc, data = finalaminoframe))


```

Create pairwise correlation matrix for supplemental material
```{r}
for (i in names(concdata[-1:-2])){
plot(concdata[[i]]~concdata[[i+1]], main=i, ylab = "oldPA", xlab= "new PA")
}
##############not right but close
corrnames<-c("Threonate", "Sucrose", "myo.Inositol","Maltose", "Glucose","Galactinol","Fructose", "Proline", "Leucine","Glycine")
corrnames
sugarcorrnames<-c("Threonate", "Sucrose", "myo.Inositol","Maltose", "Glucose","Galactinol","Fructose")
aminocorrnames<-c("Proline", "Leucine","Glycine")

library("reshape2")
totalcor<-round(cor(concdata[corrnames]),2)

get_lower_tri<-function(totalcor){
    totalcor[lower.tri(totalcor)] <- NA
    return(totalcor)
}

lowertritotal<-get_lower_tri(totalcor)
lowertritotal

totalcor2<-melt(lowertritotal, na.rm = TRUE)

pdf(file = "pairwisecorrelations.pdf", paper = "a4r",  height = 20, width = 20)
ggplot(totalcor2, aes(Var1, Var2, fill = value))+
   geom_tile(color = "white")+
   scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
   xlab("")+
   ylab("")+
  theme_minimal()+ 
   geom_text(aes(label = value), size = 3)+
   theme(axis.text.x = element_text(angle = 90, size = 10), axis.text.y = element_text(size = 10))
dev.off()



sugarcorr<-round(cor(concdata[sugarcorrnames]),2)

lowertrisugar<-get_lower_tri(sugarcorr)
lowertrisugar


sugarcorr2<-melt(lowertrisugar, na.rm = TRUE)

pdf(file = "pairwisecorrsugar.pdf", paper = "a4r",  height = 20, width = 20)
ggplot(sugarcorr2, aes(Var1, Var2, fill = value))+
   geom_tile(color = "white")+
   scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
   xlab("")+
   ylab("")+
  theme_minimal()+ 
   geom_text(aes(label = value), size = 1.5)+
   theme(axis.text.x = element_text(angle = 90, size = 5), axis.text.y = element_text(size = 5))
dev.off()



aminocorr<-round(cor(concdata[aminocorrnames]),2)


lowertriamino<-get_lower_tri(aminocorr)
lowertriamino

aminocorr2<-melt(lowertriamino, na.rm = TRUE)

pdf(file = "pairwisecorramino.pdf", paper = "a4r",  height = 20, width = 20)
ggplot(aminocorr2, aes(Var1, Var2, fill = value))+
   geom_tile(color = "white")+
   scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
   xlab("")+
   ylab("")+
  theme_minimal()+ 
   geom_text(aes(label = value), size = 1.5)+
   theme(axis.text.x = element_text(angle = 90, size = 5), axis.text.y = element_text(size = 5))
dev.off()


```

