---
title: "Fort Indiantown Gap Regal Frittilary nectar source analysis"
author: "Matthew Chmielewski"
date:  '`r format(Sys.time(), "%A, %d %B, %Y")`'
output: pdf_document
editor_options: 
  chunk_output_type:console
---

Here we Load Libraries
```{r}
packages <- c("xlsx", "purrr", "ggplot2", "dplyr", "tidyr", "RColorBrewer", "cowplot", "vegan", "lme4", "ggfortify", "ggrepel", "car", "lsmeans", "nlme", "lmerTest", "wesanderson", "ggsci")
suppressMessages(suppressWarnings(sapply(packages, require, character.only=TRUE, quietly=TRUE)))
```

I Read in  nectar concentration dataset, drop compounds with bad readings, add sex-association as a factor, write to file
```{r}
concdata<-read.xlsx("concdata.xlsx", sheetIndex  =1, header = TRUE)
concdata[is_empty(concdata)] = NA
head(concdata)
concdata2<-concdata
concdata2$Sex<-NA
concdata2[grep("Asclepias", concdata2$Species),]$Sex<-"Male"
concdata2$Sex[is.na(concdata2$Sex)]<-"Female"
write.csv(concdata2, file ="metaboliteconcdata.csv", row.names = FALSE)

concdata[,11]
```

Define amino acids and carbohydrates from the larger set of nectar compounds, then create dataframes for these sets of compounds
```{r}
aminos<-c("Arginine", "Asparagine", "Aspartate", "beta.Alanine", "Glutamine", "Glycine", "Isoleucine", "Leucine", "Lysine", "Methionine", "Ornithine", "Phenylalanine", "Proline", "Threonine", "Tryptophan", "Tyrosine", "Valine")
sugars<-c("Fructose", "Galactinol", "Glucose", "Maltose", "myo.Inositol", "Sucrose", "Threonate")
sugarframe<-concdata[sugars]
sugarframe[is.na(sugarframe)] = 0
sugarframe$totalconc<-rowSums(sugarframe[sugars])
sugarframe$species<-as.factor(concdata$Species)

aminoframe<-concdata[aminos]
aminoframe[is.na(aminoframe)] = 0
aminoframe$totalconc<-rowSums(aminoframe[aminos])
aminoframe$species<-concdata$Species

nrow(sugarframe)
sugarframe

```

Exploratory boxplots for carbohydrate concentrations by species
```{r}
pdf("sugarconcentrationsbyspecies.pdf")
for (i in names(sugarframe[,-7])){
x<-print(noquote(i))
plot(sugarbyspecies<-ggplot(data=sugarframe, aes_string("species", x)) +
geom_boxplot(fill = "gray")+
theme_bw()+
theme(axis.title.x = element_text(),
axis.title.y = element_text(),
axis.text.x  = element_text(angle=90, vjust=0.5),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
plot.title = element_text())+
ggtitle("")+
xlab("")+
ylab(i))
}
dev.off()
```

Summary of mean concentrations of compounds by species
````{r}
Fructosesummary<-sugarframe %>% group_by(species) %>% summarise(Fructose = mean(Fructose))
Sucrosesummary<-sugarframe %>% group_by(species) %>% summarise(Sucrose = mean(Sucrose))
Glucosesummary<-sugarframe %>% group_by(species) %>% summarise(Glucose = mean(Glucose))
Maltosesummary<-sugarframe %>% group_by(species) %>% summarise(Maltose = mean(Maltose))
Trehalosesummary<-sugarframe %>% group_by(species) %>% summarise(Trehalose = mean(Trehalose))
totalconcsugarssummary<-sugarframe %>% group_by(species) %>% summarise(totalconcsugars = mean(totalconc))

totalaminosummary<-aminoframe %>% group_by(species) %>% summarise(totalamimo = mean(totalconc)) 
prolinesummary<-aminoframe %>% group_by(species) %>% summarise(Proline = mean(Proline))
leucinesummary<-aminoframe %>% group_by(species) %>% summarise(Leucine = mean(Leucine))
glycinesummary<-aminoframe %>% group_by(species) %>% summarise(Glycine = mean(Glycine))

concentrationsummary<-left_join(Fructosesummary, Sucrosesummary)
concentrationsummary<-left_join(concentrationsummary, Glucosesummary)
concentrationsummary<-left_join(concentrationsummary, Maltosesummary)
concentrationsummary<-left_join(concentrationsummary, Trehalosesummary)
concentrationsummary<-left_join(concentrationsummary, totalconcsugarssummary)
concentrationsummary<-left_join(concentrationsummary, totalaminosummary)
concentrationsummary<-left_join(concentrationsummary, prolinesummary)
concentrationsummary<-left_join(concentrationsummary, leucinesummary)
concentrationsummary<-left_join(concentrationsummary, glycinesummary)

concentrationsummary

write.csv(concentrationsummary, file = "summaryofconcentrations.csv")
```

Plots of amino acid concentrations by plant species
```{r}
pdf("aminoacidconcentrationsbyspecies.pdf")
for (i in names(aminoframe[,-19])){
x<-print(noquote(i))
plot(aminobyspecies<-ggplot(data=aminoframe, aes_string("species", x)) +
geom_boxplot(fill = "gray")+
theme_bw()+
theme(axis.title.x = element_text(),
axis.title.y = element_text(),
axis.text.x  = element_text(angle=90, vjust=0.5),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
plot.title = element_text())+
ggtitle("")+
xlab("")+
ylab(i))
}
dev.off()
```

Create frames with sex coding, and long form of frames
```{r}

finalaminoframesex<-aminoframe
finalaminoframesex$sex<-aminoframe$species
levels(as.factor(finalaminoframe$species))
rownames(subset(finalaminoframe, species == c("Asclepias tuberosa", "Asclepias syriaca")))

finalaminoframesex$sex[finalaminoframesex$species == "Asclepias syriaca"]<-"M"
finalaminoframesex$sex[finalaminoframesex$species == "Asclepias tuberosa"]<-"M"
finalaminoframesex$sex[finalaminoframesex$sex != "M"] = "F"
finalaminoframesex$sex<-as.factor(finalaminoframesex$sex)


finalsugarframesex<-sugarframe
finalsugarframesex$sex<-finalaminoframesex$sex
finalaminoframesex$species<-as.factor(finalaminoframesex$species)
finalsugarframesex$species<-as.factor(finalsugarframesex$species)



##########long forms


sugarlong<-gather(finalsugarframesex, compound, value, Fructose:totalconc)
sugarlong$compound[sugarlong$compound == "totalconc"]<-"total"
aminolong<-gather(finalaminoframesex, compound, value, Arginine:totalconc)
aminolong$compound[which(aminolong$compound == "totalconc")]<-"total"

```



Create pairwise correlation matrix for supplemental material
```{r}

corrnames<-c("Threonate", "Sucrose", "myo.Inositol","Maltose", "Glucose","Galactinol","Fructose", "Proline", "Leucine","Glycine")
corrnames
sugarcorrnames<-c("Threonate", "Sucrose", "myo.Inositol","Maltose", "Glucose","Galactinol","Fructose")
aminocorrnames<-c("Proline", "Leucine","Glycine")

library("reshape2")
totalcor<-round(cor(concdata[corrnames]),2)

get_lower_tri<-function(totalcor){
    totalcor[lower.tri(totalcor)] <- NA
    return(totalcor)
}

lowertritotal<-get_lower_tri(totalcor)
lowertritotal

totalcor2<-melt(lowertritotal, na.rm = TRUE)

pdf(file = "pairwisecorrelations.pdf", paper = "a4r",  height = 20, width = 20)
ggplot(totalcor2, aes(Var1, Var2, fill = value))+
   geom_tile(color = "white")+
   scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
   xlab("")+
   ylab("")+
  theme_minimal()+ 
   geom_text(aes(label = value), size = 3)+
   theme(axis.text.x = element_text(angle = 90, size = 10), axis.text.y = element_text(size = 10))
dev.off()



sugarcorr<-round(cor(concdata[sugarcorrnames]),2)

lowertrisugar<-get_lower_tri(sugarcorr)
lowertrisugar


sugarcorr2<-melt(lowertrisugar, na.rm = TRUE)

pdf(file = "pairwisecorrsugar.pdf", paper = "a4r",  height = 20, width = 20)
ggplot(sugarcorr2, aes(Var1, Var2, fill = value))+
   geom_tile(color = "white")+
   scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
   xlab("")+
   ylab("")+
  theme_minimal()+ 
   geom_text(aes(label = value), size = 1.5)+
   theme(axis.text.x = element_text(angle = 90, size = 5), axis.text.y = element_text(size = 5))
dev.off()



aminocorr<-round(cor(concdata[aminocorrnames]),2)


lowertriamino<-get_lower_tri(aminocorr)
lowertriamino

aminocorr2<-melt(lowertriamino, na.rm = TRUE)

pdf(file = "pairwisecorramino.pdf", paper = "a4r",  height = 20, width = 20)
ggplot(aminocorr2, aes(Var1, Var2, fill = value))+
   geom_tile(color = "white")+
   scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
   midpoint = 0, limit = c(-1,1), space = "Lab", 
   name="Pearson\nCorrelation") +
   xlab("")+
   ylab("")+
  theme_minimal()+ 
   geom_text(aes(label = value), size = 1.5)+
   theme(axis.text.x = element_text(angle = 90, size = 5), axis.text.y = element_text(size = 5))
dev.off()


```

Identify outliers to remove from individual compound data prior to analysis and visualization
```{r}
#amino acids

cutofftotaa<-mean(aminolong[aminolong$compound == "total",]$value)+(sd(aminolong[aminolong$compound == "total",]$value)*4)

cutoffgly<-mean(aminolong[aminolong$compound == "Glycine",]$value)+(sd(aminolong[aminolong$compound == "Glycine",]$value)*4)

cutoffleu<-mean(aminolong[aminolong$compound == "Leucine",]$value)+(sd(aminolong[aminolong$compound == "Leucine",]$value)*4)

cutoffpro<-mean(aminolong[aminolong$compound == "Proline",]$value)+(sd(aminolong[aminolong$compound == "Proline",]$value)*4)

cutofftotaa-max(aminolong[aminolong$compound == "total",]$value)
cutoffgly-max(aminolong[aminolong$compound == "Glycine",]$value)
cutoffleu-max(aminolong[aminolong$compound == "Leucine",]$value)
cutoffpro-max(aminolong[aminolong$compound == "Proline",]$value)
#Gly,Pro, Leu all have 1 outlier

#sugars

cutofftotsugars<-mean(sugarlong[sugarlong$compound == "total",]$value)+(sd(sugarlong[sugarlong$compound == "total",]$value)*4)


cutoffglucose<-mean(sugarlong[sugarlong$compound == "Glucose",]$value)+(sd(sugarlong[sugarlong$compound == "Glucose",]$value)*4)


cutofffructose<-mean(sugarlong[sugarlong$compound == "Fructose",]$value)+(sd(sugarlong[sugarlong$compound == "Fructose",]$value)*4)


cutoffsucrose<-mean(sugarlong[sugarlong$compound == "Sucrose",]$value)+(sd(sugarlong[sugarlong$compound == "Sucrose",]$value)*4)


cutoffmaltose<-mean(sugarlong[sugarlong$compound == "Maltose",]$value)+(sd(sugarlong[sugarlong$compound == "Maltose",]$value)*4)

cutofftotsugars-max(sugarlong[sugarlong$compound == "total",]$value)
cutoffglucose-max(sugarlong[sugarlong$compound == "Glucose",]$value)
cutofffructose-max(sugarlong[sugarlong$compound == "Fructose",]$value)
cutoffsucrose-max(sugarlong[sugarlong$compound == "Sucrose",]$value)
cutoffmaltose-max(sugarlong[sugarlong$compound == "Maltose",]$value)

#none of these sugars have an outlier


```
new nested models
```{r}
length(finalaminoframesex$Leucine)

which(aminolong[aminolong$compound == "Leucine",]$value > 30)
### amino acids
finalaminoframesex[30,]

which(finalaminoframesex$Proline>cutoffpro)
#38
which(finalaminoframesex$Leucine>cutoffleu)
#38
which(finalaminoframesex$Glycine>cutoffgly)
#30
finalaminoframesex$Leucine



nestedtotalaa<-aov(finalaminoframesex$totalconc~finalaminoframesex$sex/factor(finalaminoframesex$species))
summary(nestedtotalaa)

nestedproline<-aov(finalaminoframesex[-38,]$Proline~finalaminoframesex[-38,]$sex/factor(finalaminoframesex[-38,]$species))
summary(nestedproline)

nestedleucine<-aov(finalaminoframesex[-38,]$Leucine~finalaminoframesex[-38,]$sex/factor(finalaminoframesex[-38,]$species))
summary(nestedleucine)


nestedglycine<-aov(finalaminoframesex[-30,]$Glycine~finalaminoframesex[-30,]$sex/factor(finalaminoframesex[-30,]$species))
summary(nestedglycine)

0.05/4

#Pro, Leu, Gly all significant: total AA significant but not after bonferroni correction

###sugars


nestedtotalsugars<-aov(finalsugarframesex$totalconc~finalsugarframesex$sex/factor(finalsugarframesex$species))
summary(nestedtotalsugars)


nestedglucose<-aov(finalsugarframesex$Glucose~finalsugarframesex$sex/factor(finalsugarframesex$species))
summary(nestedglucose)


nestedfructose<-aov(finalsugarframesex$Fructose~finalsugarframesex$sex/factor(finalsugarframesex$species))
summary(nestedfructose)

nestedmaltose<-aov(finalsugarframesex$Maltose~finalsugarframesex$sex/factor(finalsugarframesex$species))
summary(nestedmaltose)


nestedsucrose<-aov(finalsugarframesex$Sucrose~finalsugarframesex$sex/factor(finalsugarframesex$species))
summary(nestedsucrose)




glufru<-lm(finalsugarframesex$Fructose~finalsugarframesex$Glucose)

summary(glufru)

plot(residuals(glufru))

glufrumod<-aov(residuals(glufru)~finalsugarframesex$sex/factor(finalsugarframesex$species))

summary(glufrumod)

plot(residuals(glufrumod))


0.05/5
```



New Boxplots for publication: Create Female and Male carbohydrate and amino acid boxplots, showing individual plant species contributions
```{r}
library("scales")


speciesshape<-c(2,17,16,0,15,18)






plotcolors<-wes_palette(name = "Zissou1", n = 10, type = "continuous")
speciescolors<-plotcolors[c(1,1, 9, 10,10, 6)]

totalsugarboxplot1<-ggplot(data=subset(sugarlong, sugarlong$compound == "total"), aes(sex, value)) +
geom_boxplot(outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
annotate(geom = "text", label = "*", x =1.5, y = max(subset(sugarlong, sugarlong$compound == "total")$value)*0.9, fontface = "bold", size = 10)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_blank(),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
plot.margin = unit(c(0.5,1,0.5,1), "cm"))+
ggtitle("Total")+
xlab("")+
ylab("")

totalsugarboxplot1





glucoseboxplot1<-ggplot(data=subset(sugarlong, sugarlong$compound == "Glucose"), aes(sex, value)) +
geom_boxplot(outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
annotate(geom = "text", label = "*", x =1.5, y = max(subset(sugarlong, sugarlong$compound == "Glucose")$value)*0.9, fontface = "bold", size = 10)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_blank(),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
plot.margin = unit(c(0.5,1,0.5,1), "cm"))+
ggtitle("Glucose")+
xlab("")+
ylab("")

glucoseboxplot1


sucroseboxplot1<-ggplot(data=subset(sugarlong, sugarlong$compound == "Sucrose"), aes(sex, value)) +
geom_boxplot(width = 0.5, outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_blank(),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
plot.margin = unit(c(0.5,1,0.5,1), "cm"))+
ggtitle("Sucrose")+
xlab("")+
ylab("")

sucroseboxplot1


fructoseboxplot1<-ggplot(data=subset(sugarlong, sugarlong$compound == "Fructose"), aes(sex, value)) +
geom_boxplot(outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
annotate(geom = "text", label = "*", x =1.5, y = max(subset(sugarlong, sugarlong$compound == "Fructose")$value)*0.9, fontface = "bold", size = 10)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_blank(),
axis.text.x  = element_text(face = "bold", size = 14, hjust = 0.5),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
plot.margin = unit(c(0.5,1,0.5,1), "cm"))+
ggtitle("Fructose")+
xlab("")+
ylab("")

fructoseboxplot1



galactinolboxplot1<-ggplot(data=subset(sugarlong, sugarlong$compound == "Galactinol"), aes(sex, value)) +
geom_boxplot(outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
annotate(geom = "text", label = "*", x =1.5, y = max(subset(sugarlong, sugarlong$compound == "Galactinol")$value)*0.9, fontface = "bold", size = 10)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_blank(),
axis.text.x  = element_text(face = "bold", size = 14, hjust = 0.5),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
plot.margin = unit(c(0.5,1,0.5,1), "cm"))+
ggtitle("Galactinol")+
xlab("")+
ylab("")

galactinolboxplot1



maltoseboxplot1<-ggplot(data=subset(sugarlong, sugarlong$compound == "Maltose"), aes(sex, value)) +
geom_boxplot(width = 0.5, outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_blank(),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
plot.margin = unit(c(0.5,1,0.5,1), "cm"))+
ggtitle("Maltose")+
xlab("")+
ylab("")

maltoseboxplot1



threonateboxplot1<-ggplot(data=subset(sugarlong, sugarlong$compound == "Threonate"), aes(sex, value)) +
geom_boxplot(width = 0.5, outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_blank(),
axis.text.x  = element_blank(),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
plot.margin = unit(c(0.5,1,0.5,1), "cm"))+
ggtitle("Threonate")+
xlab("")+
ylab("")

threonateboxplot1
  
   




myo.Inositolboxplot1<-ggplot(data=subset(sugarlong, sugarlong$compound == "myo.Inositol"), aes(sex, value)) +
geom_boxplot(width = 0.5, outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_blank(),
axis.text.x  = element_text(face = "bold", size = 14, hjust = 0.5),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5),
plot.margin = unit(c(0.5,1,0.5,1), "cm"))+
ggtitle("Myo-Inositol")+
xlab("")+
ylab("")

myo.Inositolboxplot1



totalaminoboxplot1<-ggplot(data=subset(aminolong, aminolong$compound == "total"), aes(sex, value)) +
geom_boxplot(width = 0.5, outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 14, hjust = 0.5),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
axis.text.x  = element_blank(),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5))+
ggtitle("Total")+
xlab("")+
ylab("")

totalaminoboxplot1


leucineboxplot1<-ggplot(data=subset(aminolong, aminolong$compound == "Leucine")[-38,], aes(sex, value)) +
geom_boxplot(width = 0.5, outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
scale_y_continuous(limits= c(15, 25), breaks = breaks_width(5))+
annotate(geom = "text", label = "*", x =1.5, y = max(subset(aminolong, aminolong$compound == "Leucine")[-38,]$value)*0.95, fontface = "bold", size = 10)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 16, hjust = 0.5),
axis.text.x  = element_text(face = "bold", size = 14),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5))+
ggtitle("Leucine")+
xlab("")+
ylab("")

leucineboxplot1
  


prolineboxplot1<-ggplot(data=subset(aminolong, aminolong$compound == "Proline")[-38,], aes(sex, value)) +
geom_boxplot(width = 0.5, outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
scale_y_continuous(limits= c(0, 60), breaks = breaks_width(20))+
annotate(geom = "text", label = "*", x =1.5, y = max(subset(aminolong, aminolong$compound == "Proline")[-38,]$value)*0.95, fontface = "bold", size = 10)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(face = "bold", size = 14, hjust = 0.5),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
axis.text.x  = element_blank(),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "none",
plot.title = element_text(face = "bold", size = 16, hjust = 0.5))+
ggtitle("Proline")+
xlab("")+
ylab("")

prolineboxplot1




glycineboxplot1a<-ggplot(data=subset(aminolong, aminolong$compound == "Glycine")[-30,], aes(sex, value)) +
geom_boxplot(width = 0.5, outlier.shape = NA)+
geom_point(aes(color = species, shape = species), cex = 2, position = position_dodge(width = 0.8))+
scale_shape_manual(values = speciesshape)+
scale_color_manual(values = speciescolors)+
scale_y_continuous(limits= c(35, 60), breaks = breaks_width(10))+
annotate(geom = "text", label = "*", x =1.5, y = max(subset(aminolong, aminolong$compound == "Glycine")[-30,]$value)*0.95, fontface = "bold", size = 10)+
theme_bw()+
theme(axis.title.x = element_blank(),
axis.title.y = element_text(),
axis.text.x  = element_text(face = "bold", size = 14, hjust = 0.5),
axis.text.y = element_text(face = "bold", size = 14, color = "black"),
panel.grid.minor.x=element_blank(),
panel.grid.major.x=element_blank(),
panel.grid.minor.y=element_blank(),
panel.grid.major.y=element_blank(),
legend.position = "right",
legend.title = element_blank(),
legend.text = element_text(face = "italic", size = 16),
plot.title = element_text(face = "bold", size = 16, hjust = 0.5))+
ggtitle("Glycine")+
xlab("")+
ylab("")

glycineboxplot1a
plotlegend<-get_legend(glycineboxplot1a)

glycineboxplot1<-glycineboxplot1a+theme(legend.position = "none")

glycineboxplot1
  
aminoupdate1<-plot_grid(totalaminoboxplot1, prolineboxplot1, NULL,  glycineboxplot1, leucineboxplot1, NULL, align = "hv", ncol = 3, rel_widths = c(1,1,1), labels = c("a)", "b)", "", "c)", "d)", ""), label_x = 0.2, label_size= 16)
aminoupdate1

aminoupdate1final<-aminoupdate1+draw_grob(plotlegend, hjust = -0.35)
aminoupdate1final<-aminoupdate1final+draw_text("Concentration (µg/mL)", x = 0.02,  y = 0.5, size = 14, angle =90, fontface= "bold")

aminoupdate1final

sugarupdate1<-plot_grid(totalsugarboxplot1, glucoseboxplot1, NULL, sucroseboxplot1,  maltoseboxplot1, NULL,  fructoseboxplot1, NULL, NULL, align = "v", ncol = 3, nrow = 4, rel_widths = c(1,1,0.65), axis = "left", labels = c("a)", "b)", "", "c)", "d)", "", "e)", "",""), label_x = 0.2, label_y = 1.01, label_size = 16)

sugarupdate1

sugarupdate1final<-sugarupdate1+draw_grob(plotlegend, hjust = -0.1, vjust = 0.125)
sugarupdate1final<-sugarupdate1final+draw_text("Concentration (µg/mL)", x = 0.02,  y = 0.5, size = 16, angle =90, fontface= "bold")

sugarupdate1final


pdf(file = "aminoplotnew.pdf", width = 9, height = 7)
aminoupdate1final
dev.off()


pdf(file = "sugarplotnew.pdf", width = 8.5, height = 12)
sugarupdate1final
dev.off()

plot(plotlegend)

packageVersion("stats")


```
